%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\skillItem}[2]{
  \item\small{
    \textbf{#1:}{ #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/mparra-mpz}{\Large Manuel Parra Z\'u\~niga}} & Email : \href{mailto:mparra.mpz@gmail.com}{mparra.mpz@gmail.com}\\
  \href{https://www.linkedin.com/in/mparra-mpz}{https://www.linkedin.com/in/mparra-mpz} & Mobile : +56 9 9475 6894 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidad Cat\'olica del Norte}{Antofagasta, Chile}
      {Bachelor of Computer Science Engineering}{March. 2003 -- December. 2009}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {ALMA Observatory}{San Pedro de Atacama, Antofagasta}
      {Software Engineer}{November 2009 - November 2015}
      \resumeItemListStart
        \resumeItem{Maintain the continuous operation of the observatory performing tasks like install the new software versions, investigate software bugs with external developers.}
        \resumeItem{Test the new features in the ALMA software focussing in the Control and Correlator subsystems.}
        \resumeItem{Lead software developer for the antenna's receptor.}
        \resumeItem{Occasionally lead the software team and attend to science and engineering meetings to report the status of the software bugs.}
      \resumeItemListEnd

    \resumeSubheading
      {Cerro Armazones Observatory}{Cerro Amarzones, Antofagasta}
      {Software Developer}{December 2008 - September 2009}
      \resumeItemListStart
        \resumeItem{Update components over ALMA Common Software (ACS) from ACS 4.0 to ACS 9.1.}
        \resumeItem{Update the C++ code standards from C++03 to C++11.}
        \resumeItem{Develop code for the mount, CCD camera, rotators, weather station and create the user interfaces to perform scientific observations using those devices.}
      \resumeItemListEnd      
  \resumeSubHeadingListEnd


%--------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \skillItem{C++}
    {Write and maintain code for hardware devices used in ALMA observatory, lead programmer for the antenna's receptors devices.}
    \skillItem{C}{Maintain kernel modules code used in ALMA observatory, basic knowledge of RT-Preempt.}
    \skillItem{Java}{Maintain code for ALMA's observing modes (business logic). Development of personal projects with Build Tools (maven), ORM frameworks (hibernate) and RPC framework (ICE).}
    \skillItem{Python}{Development of scripts to help the science operation in ALMA observatory. Code for graphical user interface using Qt tools.}
    \skillItem{Development Tools}{Integrated Development Environment(IDE) mainly Eclipse, a basic knowledge of Netbeans. Version Control System like CVS, SVN, GIT, etc. Network Management System like Zenoss, Cacti and Nagios.}
    \skillItem{Operating Systems}{Advance user experience in GNU/linux distributions like Redhat, Debian, Gentoo, etc.}
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
%\section{Projects}
%  \resumeSubHeadingListStart
%    \resumeSubItem{QuantSoftware Toolkit}
%      {Open source python library for financial data analysis and machine learning for finance.}
%    \resumeSubItem{Github Visualization}
%      {Data Visualization of Git Log data using D3 to analyze project trends over time.}
%    \resumeSubItem{Recommendation System}
%      {Music and Movie recommender systems using collaborative filtering on public datasets.}
%    \resumeSubItem{Mac Setup}
%      {Book that gives step by step instructions on setting up developer environment on Mac OS.}
%  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
